Computational methods in landscape ecology

### 2024-09-18 Sections/03-connectivity.qmd
Remove trailing whitespaces

Landscape connectivity describes how landscapes facilitate or impede movement among resource patches [@Taylor1993ConnectivityVital; @Taylor2006LandscapeConnectivity].
It underpins ecosystem functionality, maintains biodiversity and populations, and plays a large role in many conservation actions [@CorreaAyram2016HabitatConnectivity; @Hilty2020GuidelinesConserving] and multiple approaches how to measure connectivity were developed [@Simpkins2018AssessingPerformance; @Keeley2021ConnectivityMetrics].
Connectivity can be divided into structural and functional connectivity.
Structural connectivity describes the physical arrangement of landscape elements, focusing on spatial aspects such as continuity and adjacency. 
It is solely a landscape feature and independent of species' characteristics [@Tischendorf2000UsageMeasurement; @CorreaAyram2016HabitatConnectivity]. 
Functional connectivity, in contrast, integrates landscape structure with the perceptual, behavioural, and dispersal characteristics of species, making it both species- and landscape-specific [@Adriaensen2003ApplicationLeastcost; @Taylor2006LandscapeConnectivity].

>>>>

Landscape connectivity describes how landscapes facilitate or impede movement among resource patches [@Taylor1993ConnectivityVital; @Taylor2006LandscapeConnectivity].
It underpins ecosystem functionality, maintains biodiversity and populations, and plays a large role in many conservation actions [@CorreaAyram2016HabitatConnectivity; @Hilty2020GuidelinesConserving].
Thus, multiple approaches how to measure connectivity were developed [@Simpkins2018AssessingPerformance; @Keeley2021ConnectivityMetrics].
Connectivity can be divided into structural and functional connectivity.
Structural connectivity describes the physical arrangement of landscape elements, focusing on spatial aspects such as continuity and adjacency.
It is solely a landscape feature and independent of species' characteristics [@Tischendorf2000UsageMeasurement; @CorreaAyram2016HabitatConnectivity].
Functional connectivity, in contrast, integrates landscape structure with the perceptual, behavioural, and dispersal characteristics of species, making it both species- and landscape-specific [@Adriaensen2003ApplicationLeastcost; @Taylor2006LandscapeConnectivity].
